---
title: "p8105_hw6_wy2369"
output: github_document
author: Wenjing Yang
date: "2022-11-29"
---

```{r, include=FALSE}
library(tidyverse)
library(viridis)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1


# Problem 2

### Read and clean

Create a `city_state` variable and a `homicide_status` (binary) variable indicating whether the homicide is solved. Number 0 means "unsolved" and 1 means "solved"

Then omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Filter whom victim_race is white or black, and convert `victim_age` to numerical variable. Drop NAs which shown in `victim_age`. 

```{r,message=FALSE}
homicide_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, ",", state),
    victim_age = as.numeric(victim_age),
    homicide_status =  ifelse(disposition != "Closed by arrest", 0, 1)) %>% 
  filter(city_state != "Dallas,TX" & city_state != "Phoenix,AZ" & city_state !="Kansas City,MO" & city_state != "Tulsa,AL") %>% 
  filter(victim_race == "White" | victim_race == "Black") %>% 
  drop_na(victim_age)
```

### Fit a logistic regression for one city

Use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and `victim_age`, `victim_sex` and `victim_race` as predictors. Save the output of `glm` as an R object and apply the `broom::tidy` to tidy the data. 

```{r}
baltimore_reg = 
  homicide_data %>% 
  filter(city_state == "Baltimore,MD") %>% 
  glm(homicide_status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    Odds_ratio = exp(estimate),
    Lower_CI = exp(estimate - 1.96 * std.error),
    Upper_CI = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, estimate, Odds_ratio, Lower_CI, Upper_CI) %>% 
  knitr::kable(digits = 3)

baltimore_reg
```

From the table, I obtain the estimate is **-0.854**，adjusted odds_ratio is **0.426** and confidence interval is **(0.325, 0.558)** for solving homicides comparing male victims to female victims keeping all other variables fixed.

### Fit a logistic regression for all cities

```{r}

```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

