---
title: "p8105_hw6_wy2369"
output: github_document
author: Wenjing Yang
date: "2022-11-29"
---

```{r, include=FALSE}
library(tidyverse)
library(viridis)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1


# Problem 2

### Read and clean

Create a `city_state` variable and a `homicide_status` (binary) variable indicating whether the homicide is solved. 

Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. 

```{r}
homicide_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, ",", state),
    homicide_status =  ifelse(disposition != "Closed by arrest", "unsolved", "solved")) %>% 
  filter(city_state != "Dallas,TX" & city_state != "Phoenix,AZ" & city_state !="Kansas City,MO" & city_state != "Tulsa,AL")
```



For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.