---
title: "p8105_hw6_wy2369"
output: github_document
author: Wenjing Yang
date: "2022-11-29"
---

```{r, include=FALSE}
library(tidyverse)
library(viridis)
library(patchwork)
library(olsrr)
library(mgcv)
library(modelr)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

### Draw bootstrap samples

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Distribution for $\hat{r}^2$ value

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

### Distribution for $\log(\beta_0 * \beta1)$

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

# Problem 2

### Read and clean data

Create a `city_state` variable and a `homicide_status` (binary) variable indicating whether the homicide is solved. Number 0 means "unsolved" and 1 means "solved"

Then omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Filter whom victim_race is white or black, and convert `victim_age` to numerical variable. Drop NAs which shown in `victim_age`. 

```{r,message=FALSE}
homicide_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, ",", state),
    victim_age = as.numeric(victim_age),
    homicide_status =  ifelse(disposition != "Closed by arrest", 0, 1)) %>% 
  filter(city_state != "Dallas,TX" & city_state != "Phoenix,AZ" & city_state !="Kansas City,MO" & city_state != "Tulsa,AL") %>% 
  filter(victim_race == "White" | victim_race == "Black") %>% 
  drop_na(victim_age)
```

### Fit a logistic regression for one city

Use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and `victim_age`, `victim_sex` and `victim_race` as predictors. Save the output of `glm` as an R object and apply the `broom::tidy` to tidy the data. 

```{r}
baltimore_reg = 
  homicide_data %>% 
  filter(city_state == "Baltimore,MD") %>% 
  glm(homicide_status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    odds_ratio = exp(estimate),
    lower_CI = exp(estimate - 1.96 * std.error),
    upper_CI = exp(estimate + 1.96 * std.error)
  ) %>% 
  filter(term == "victim_sexMale") %>% 
  select(term, estimate, odds_ratio, lower_CI, upper_CI) %>% 
  knitr::kable(digits = 3)

baltimore_reg
```

From the table, I obtain the estimate is **-0.854**，adjusted odds_ratio is **0.426** and 95% confidence interval is **(0.325, 0.558)** for solving homicides comparing male victims to female victims keeping all other variables fixed.

### Fit a logistic regression for each cities

Run `glm` for each of the cities in the dataset and use `map` and `unnest` functions to create a tidy dataframe with estimates, odds ratios and confidence intervals for each city.

```{r}
homicide_reg = 
  homicide_data %>% 
  nest(data = -city_state) %>% 
  mutate(
    results = map(.x = data ,~glm(homicide_status ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    results = map(results, broom::tidy)) %>% 
  unnest(results) %>%
  mutate(
    odds_ratio = exp(estimate),
    lower_CI = exp(estimate - 1.96 * std.error),
    upper_CI = exp(estimate + 1.96 * std.error)
  ) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, estimate, odds_ratio, lower_CI, upper_CI) 

homicide_reg %>%
  knitr::kable(digits = 3)
```

This table shows estimates, odds ratios and 95% confidence intervals for each city for solving homicides comparing male victims to female victims keeping all other variables fixed.


### Create a plot with errorbar

The plot shows the estimated odds ratios and 95% confidence intervals for each city. 

```{r}
homicide_reg %>%
  ggplot(aes(x = fct_reorder(city_state,odds_ratio), y = odds_ratio)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_CI, ymax = upper_CI)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "The estimated odds ratios and confidence intervals for each city",
       x = "City, State",
       y = "Estimated odds ratios") 
```

Based on this plot, New York,NY might have the lowest estimated odds ratio for solving homicides comparing male victims to female victims, and Albuquerque,NM might have highest estimated odds ratio comparing male victims to female victims. There are some wide confidence intervals shown in the plot, for example Fresno,CA, Stockton,CA and Albuquerque,NM. 


# Problem 3

### Load and clean data

Load data from `birthweight.csv` and convert variables numeric to factor, for example babysex, frace, malform and mrace. Then check for missing data using this code chunk.

```{r}
birthweight_data = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
   mutate(
     babysex = as.factor(babysex),
     frace = as.factor(frace),
     malform = as.factor(malform),
     mrace = as.factor(mrace))

skimr::skim(birthweight_data)
```

Based on these results, there is no missing data in this dataset.

### Fit a regression model

Try to fit a regression model using `lm`, and preform the stepwise model selection using `step`.

```{r}
all_fit = lm(bwt~ ., data = birthweight_data) 
  
step(all_fit, direction = "both")
```

The first step is put all variables in lm function and try to fit `all_fit` model, and then I use stepwise model selection to calculate and compare AIC to find the best model. 

The stepwise model selection is a data-driven model-building process. Based on the results, the best model using stepwise should be bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken. 

### Make a plot of residuals against fitted values

Using this code chunk to make a plot of model residuals against fitted values – use `add_predictions` and `add_residuals` in making this plot.

```{r}
stepwise_fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_data)


birthweight_data %>% 
  modelr::add_residuals(stepwise_fit) %>%
  modelr::add_predictions(stepwise_fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha =.3) +
  labs( 
    x= "Fitted Values", 
    y = "Residuals",
    title = "Residuals against Fitted values on stepwise_fit") +
  geom_line(aes(y = 0), color = "red")
```

### Compare my model to two others

This code chunk is to fit two other regression models using `lm`, and make this comparison in terms of the cross-validated prediction error using `crossv_mc`.

`model_1`: use length at birth and gestational age as predictors (main effects only)
`model_2`: use head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = birthweight_data)
model_2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birthweight_data)

cv_df = 
  crossv_mc(birthweight_data, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
    fit_1 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit_2 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x)),
    myfit = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x))
  ) %>% 
   mutate(
     rmse_fit_1 = map2_dbl(.x = fit_1, .y = test, ~rmse(model = .x, data = .y)),
     rmse_fit_2 = map2_dbl(.x = fit_2, .y = test, ~rmse(model = .x, data = .y)), 
     rmse_myfit = map2_dbl(.x = myfit, .y = test, ~rmse(model = .x, data = .y))
  )
```

### Make a plot to check RMSE

Compare rmse values of these three models, I use `geom_violin` function to make this graph in the code chunk below.

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model,y =rmse,color = model))+
  geom_violin()+
  labs(
    y= "rmse", 
    x = "Models",
    title = "Comparison of RMSE for three models") 
```

Lower rmse value means better regression model, so based on this plot, `myfit` has the lowest rmse value on average and `fit_1` has the greatest rmse value on average among these three models. Although the rmse value of `myfit` is about 275 which is pretty huge for a good regression model, `myfit` is still the best fit compared to two others.  


